Bird beak's elaboration and innovation

### 2022-02-10 Analysis/09-Figure3.Rmd
ugh...

```{r, echo = FALSE, eval = FALSE}

one.plot.correlations <- function(cor.results, col.sub, col.fun = colour.palette, legend.pos = "topleft", pt.cex = 0.5, legend.cex = 0.5, ID, ...) {

@@

    ## Plotting the results
    plot(cor.results$x, cor.results$y, pch = 19, xlab = ifelse(), ylab = ifelse(ID == 1 || ID == 5, "exploration", ""), main = cor.results$main, cex = pt.cex, col = col_vector)

@@

par(mfrow = c(2, 4))
lims <- list(x = range(global_data$x),
             y = range(global_data$y))

## Getting the subsets for the colouring
col_subs <- c(split(shapespace$level2, f = shapespace$level1)[-1], "phylogeny" = list(shapespace$level1))

@@

for(i in 1:8) {
    plot.correlations(super_phylo_cor[[i]], xlim = lims$x, ylim = lims$x, tree = NULL, col.sub = col_subs[[i]], legend.pos = legends_pos[i])
}

```

>>>>

```{r, echo = FALSE, eval = FALSE}
one.plot.correlations <- function(cor.results, col.sub, col.fun = colour.palette, legend.pos = "topleft", pt.cex = 0.5, legend.cex = 0.5, ID, ...) {

@@

    ## Plotting the results

    ## Selecting the x and y axis base on plot ID
    select.x <- function(ID, yes = "", no = "") {
        ifelse(ID %in% c(5:8), yes, no)
    }
    select.y <- function(ID, yes = "", no = "") {
        ifelse(ID == 1 || ID == 5, yes, no)
    }

    par(mar = c(select.x(ID, 4, 1), select.y(ID, 4, 1), 3, 1)+0.1)
    plot(cor.results$x, cor.results$y, pch = 19,
        xlab = select.x(ID, "elaboration"),
        ylab = select.y(ID, "explortation"),
        main = strsplit(cor.results$main, split = ":")[[1]][1],
        cex = pt.cex, col = col_vector,
        ...)

    if(!is.null(col.sub)) {
        legend_text <- levels(col_sub)
        if(length(empty <- which(legend_text == "")) > 0) {
            legend_text[empty] <- "other"
        }
        ## Adding the legend
        legend(x = legend.pos, legend = legend_text, pch = 19, cex = legend.cex, col = col_avail, bg = "white")
    }

@@

par(mfrow = c(2, 4))
## Getting the subsets for the colouring
col_subs <- c(split(shapespace$level2, f = shapespace$level1)[-1], "phylogeny" = list(shapespace$level1))

@@

for(i in 1:8) {
    one.plot.correlations(super_phylo_cor[[i]],col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.8, legend.cex = 0.8)
}
```

## Figure 3c

```{r, echo = FALSE, eval = FALSE}
par(mfrow = c(2, 4))
## Getting the subsets for the colouring
col_subs <- c(split(shapespace$level2, f = shapespace$level1)[-1], "phylogeny" = list(shapespace$level1))

## Set the vector of legend positions
legends_pos <- c("bottomright", "topright", "topright", "topleft", "topleft", "topright", "bottomright", "bottomright")

for(i in 1:8) {
    one.plot.correlations(super_group_cor[[i]], col.sub = col_subs[[i]], legend.pos = legends_pos[i], ID = i, pt.cex = 0.8, legend.cex = 0.8)
}
```
